Owl occupancy in three of El Salvador's protected areas from 2003 to 2013

### 2021-01-31 manuscript_working/ms_working_RMD.Rmd
put map into manuscript
updated map legend in ms
update format: table 1

```{r}
library(pander)
Habitat <- c("Reforested Deciduous Forest",
             "Semi-Deciduous Forest",
             "Cloud Forest",
             "Pine/Oak Forest",
             "Alluvial Forest with Secondary Growth",
             "Alluvial Forest")
Latitude <- c("xxx", "XXX", "XXX", "XXX", "XXX", "XXX")
Longitude <- c("xxx", "XXX", "XXX", "XXX", "XXX", "XXX")
Elevation <- c("xxx", "xxx", "xxx", "xxx", "xxx", "xxx")
Route <- c("EI-1", "EI-2", "M-1", "M-2", "N-1", "N-2")
Area <- c("El Imposible", "NP", 
          "Montecristo", "NP", "Nancuchiname", "Forest")
#parkTable <- as.data.frame(matrix(
#  c(NamePark, NameRoute, Latitude, Longitude, Habitat), byrow = T, nrow = 5, ncol = 7))
parkTable <- data.frame(Route, Latitude, Longitude, Elevation, Habitat)
pander(parkTable)

@@

![1XX. Map of El Salvador. Owl surveys were conducted from 2003 to 2013 in three different protected areas within El Salvador: El Imposible National Park (EI-1 and EI-2), Montecristo National Park (M-1 and M-2) and Nancuchiname Forest (N-1 and N-2).   \label{psi_means}](../output/figures/psi_means-12.png)

>>>>

```{r}
library(pander)
Habitat <- c("Reforested deciduous forest",
             "Semi-deciduous forest",
             "Cloud forest",
             "Pine/oak forest",
             "Alluvial forest with secondary growth",
             "Alluvial forest")
Latitude <- c("13xx 50.75'", "13xx 51.38'", 
              "14xx 24.88'", "14xx 23.19'", 
              "13xx 19.95'", "13xx 22.03'")
Longitude <- c("89xx 59.74'", "89xx 58.24'", 
               "89xx 21.63'", "89xx 22.33'", 
               "88xx 43.63'", "88xx 43.30'")
Elevation <- c("609", "958", "2111", "1755", "3", "2")
Route <- c("EI-1", "EI-2", "M-1", "M-2", "N-1", "N-2")
Area <- c("El Imposible", "NP", 
          "Montecristo", "NP", "Nancuchiname", "Forest")
#parkTable <- as.data.frame(matrix(
#  c(NamePark, NameRoute, Latitude, Longitude, Habitat), byrow = T, nrow = 5, ncol = 7))
parkTable <- data.frame(Route, Latitude, Longitude, Elevation, Habitat)
pander(parkTable)

@@

![1XX. Map of El Salvador. Owl surveys were conducted from 2003 to 2013 in three different protected areas within El Salvador: El Imposible National Park (EINP), Montecristo National Park (MNP) and Nancuchiname Forest (NF).   \label{map}](../output/figures/map-1.png)
